The Role of Advection Versus Diffusion in Intraventricular Transport

### 2025-02-23 paper/main.tex
minor update

The tangential stresses $\btau = \tau\lambda(\xx) P_{\nn}(\rr)$ that represent the cilia
motion differ for the cilia regions. We heuristically determined the constant $\tau= 0.65$ mPa
and the spatially varying function $\lambda(\xx)$. The definitions of $\rr$ and $\lambda(\xx)$
for the different cilia populations are summarized in~\Cref{tab:r_vector_and_lambda_function}.
\begingroup
\setlength{\tabcolsep}{20pt}
\renewcommand{\arraystretch}{1.5}
\begin{table}[H]
    \centering
    \caption{Definitions of $\rr$ and $\lambda(\xx)$ used in for the cilia tangential 
    traction boundary condition $\btau = \tau\lambda(\xx)P_{\nn}(\rr)$,
    where $\tau=0.65$ mPa. The $x-$coordinates $x_{0, i}$ and $x_{e, i}$ define 
    the cilia domain in the dorsal ($i=d$) and ventral ($i=v$) regions of 
    the middle ventricle.}\label{tab:r_vector_and_lambda_function}
    \begin{tabular}{lcc}
        \toprule
        Cilia population & $\rr$ & $\lambda(\xx)$ \\
        \midrule 
        Anterior region, anterior ventricle 
        & $-(1, 0, 1)$ & $\frac{2}{5}$ \\
        Posterior region, anterior ventricle
        & $\ \ \ (1, 0, 1)$ & 1 \\
        Dorsal region, middle ventricle     
        & $-(1, 0, 1)$
        & $\lambda(\xx)=\frac{11}{4}\left(\frac{x-x_{0, d}}{x_{e, d} - x_{0, d}}\right)$\\
        Ventral region, middle ventricle    
        & $\ \ \ (1, 0, 1)$
        & $\lambda(\xx) = \frac{1}{2}\left(1 - \frac{x-x_{0, v}}{x_{e, v} - x_{0, v}}\right)$ \\
        \bottomrule
    \end{tabular}
\end{table}
\endgroup

>>>>

The tangential stresses $\btau = \tau\lambda(\xx) P_{\nn}(\rr)$ that represent the cilia
motion differ for the cilia regions. We heuristically determined the constant $\tau= 0.65$ mPa
and the spatially varying function $\lambda(\xx)$. The definitions of $\rr$ and $\lambda(\xx)$
for the different cilia populations are summarized in~\Cref{tab:r_vector_and_lambda_function}.
\begingroup
\setlength{\tabcolsep}{20pt}
\renewcommand{\arraystretch}{1.5}
\begin{table}[H]
    \centering
    \caption{Definitions of $\rr$ and $\lambda(\xx)$ used in for the cilia tangential 
    traction boundary condition $\btau = \tau\lambda(\xx)P_{\nn}(\rr)$,
    where $\tau=0.65$ mPa. The $x-$coordinates $x_{0, i}$ and $x_{e, i}$ define 
    the cilia domain in the dorsal ($i=d$) and ventral ($i=v$) regions of 
    the middle ventricle.}\label{tab:r_vector_and_lambda_function}
    \begin{tabular}{lcc}
        \toprule
        Cilia population & $\rr$ & $\lambda(\xx)$ \\
        \midrule 
        Anterior region, anterior ventricle 
        & $-(1, 0, 1)$ & $\frac{2}{5}$ \\
        Posterior region, anterior ventricle
        & $\ \ \ (1, 0, 1)$ & 1 \\
        Dorsal region, middle ventricle     
        & $-(1, 0, 1)$
        & \frac{11}{4}\left(\frac{x-x_{0, d}}{x_{e, d} - x_{0, d}}\right)$\\
        Ventral region, middle ventricle    
        & $\ \ \ (1, 0, 1)$
        & \frac{1}{2}\left(1 - \frac{x-x_{0, v}}{x_{e, v} - x_{0, v}}\right)$ \\
        \bottomrule
    \end{tabular}
\end{table}
\endgroup
